Mamary Gland Development Exploratory Data Analysis

### 2017-06-26 src/QCAnalysis.Rmd
bugfix

```{r}
stopifnot(identical(as.character(pD$barcode),colnames(m)))
stopifnot(identical(as.character(fD$id),rownames(m)))
out <- list()
out[[1]] <- m
out[[2]] <- pD
out[[3]] <- fD
saveRDS(out,file="../data/Robjects/secondRun_2500/ExpressionList_QC.rds")
```

>>>>

```{r}
stopifnot(identical(as.character(pD$barcode),colnames(m)))
stopifnot(identical(as.character(fD$id),rownames(m)))
out <- list()
out[["counts"]] <- m
out[["phenoData"]] <- pD
out[["featureData"]] <- fD
saveRDS(out,file="../data/Robjects/secondRun_2500/ExpressionList_QC.rds")
```
